Search-based Synthesis of Network Intrusion Detection Rules

### 2019-09-07 paper/paper.tex
pass on example

@@

Figure~\ref{fig:synflood-example} shows an
example rule of Suricata~\cite{suricata}, a popular open-source
\nids{}, maintained by the Open Information Security Foundation
(OISF)~\cite{oisf}. This example shows how Suricata can be used to
protect against SYN flood attacks.\Fix{explain the structure of the rule.}

@@

\Mar{Lucas/Guilherme (CRI): por favor, explique o formato de uma regra do
  Suricata e, em seguida, explique esta regra, detalhando o
  significado de cada propriedade/campo.}

@@

\Mar{Lucas/Guilherme (CRI): vcs. precisam dar pontape inicial (bom
  exercicio) propondo perguntas de pesquisa. Eu faco ajustes em seguida.}

>>>>

\Mar{Lucas/Guilherme, verifique se isto esta correto}
Figure~\ref{fig:synflood-example} shows an example rule of
Suricata~\cite{suricata}, a popular open-source \nids{} maintained by
the Open Information Security Foundation (OISF)~\cite{oisf}. This
example shows how Suricata can be used to protect organizations
against one kind of attack. The rule is divided in three
parts~\cite{suri-rule-format}--action, header, and rule options. The
action part always appears as the first word in the rule. In this
case, \CodeIn{alert}. An action denotes the task that needs to be
executed if the rule pattern is satisfied. So, in this case, a message
will be sent to sys admins if the rule pattern is satisfied. The
header comes after the action in the rule description. It restricts
the information flow covered by the rule. For this rule, the header is
\CodeIn{tcp \$HOME\_NET any -> \$EXTERNAL\_NET any} indicating that
the rule inspects \CodeIn{tcp} traffic flowing from any port in the
home network to any other address outside the home network. The rule
options come after the header. It is a semi-colon-separated sequence
of key-value pairs characterizing the pattern of attack. For example,
\Mar{Lucas/Guilherme (IMP): explique o que cada propriedade faz...}

\Mar{------------------------------ parei aqui}

@@

@@

@@

\Mar{Lucas/Guilherme (CRI): precisamos dar pontape inicial propondo
  perguntas de pesquisa. Eu faco ajustes em seguida.}
